Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-18 cloneoverflow-latex/cloneoverflow.tex
Restructured Section 2.
Moved patterns of online cloning to Section 2 (2.4.1)
Small change in the code example.

\begin{figure*}
	\begin{lstlisting}
          /* Code in Stack Overflow post ID 22315734 */                  /* WritableComparator.java (2016-09-26) */
          public int compare (byte[] b1,int s1,int l1,                   public int compare(byte[] b1,int s1,int l1,
                              byte[] b2,int s2,int l2) {                                    byte[] b2,int s2,int l2) {
            try {                                                          try {
              buffer.reset(b1,s1,l1); /* parse key1 */                       buffer.reset(b1,s1,l1); /* parse key1 */
              key1.readFields(buffer);                                       key1.readFields(buffer);
              buffer.reset(b2,s2,l2); /* parse key2 */                       buffer.reset(b2,s2,l2); /* parse key2 */
              key2.readFields(buffer);                                       key2.readFields(buffer);
            } catch (IOException e) {                                        buffer.reset(null,0,0); /* clean up reference */
              throw new RuntimeException(e);                               } catch (IOException e) {
            }                                                                throw new RuntimeException(e);
            return compare(key1,key2); /* compare them */                  }
          }                                                                return compare(key1, key2); /* compare them */
	                                                                       }
	\end{lstlisting}
	\caption{A motivating example of the two code fragments of
          {\small\texttt{WritableComparator.java}}. The one from the
          Stack Overflow post 22315734 (left) is outdated when compared to
          its latest version in the \textsf{hadoop} code base
          (right).}
	\label{fig:before-after}
\end{figure*}

@@

@@

We were aware of effects of configurations to clone detection results
and the importance of searching for optimised configurations in
empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space
of at least 15 Simian and 5 NiCad parameters, we are unable to search
for the best configurations of the tools. Thus, we decided to
configure Simian and NiCad using two established configurations:
(1)~the tools' default configurations chosen by the tools' creators
(denoted as \textit{D}), and (2)~the discovered configurations for
Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
of optimising clone detectors' configurations based on clone agreement
(denoted by \textit{E}). The details of the two configurations are
described in \Cref{t:param_tuning}. Having two clone detectors, Simian
(denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two
chosen configurations (\textit{D} and \textit{E}) each, we used
Bellon's good and ok-match for agreement in four possible pair-wise
combinations: $S_{D}$--$N_{D}$, $S_{D}$--$N_{E}$, $S_{E}$--$N_{D}$,
and $S_{E}$--$N_{E}$.

@@

The statistics on clones obtained from running Simian and NiCad are
presented in \Cref{tab:raw_stats}. Simian in the default configuration
($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
144,064 Stack Overflow snippets, associated with 92 Qualitas
projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
snippets containing clones associated with 111 Qualitas
projects. NiCad in the default configuration ($N_D$) reported clones
between 1,392 Stack Overflow code snippets and 82 Qualitas
projects. NiCad in the EvaClone configuration ($N_E$) reported the
largest number of 12,886 cloned snippets mainly due to the more
relaxed configuration. The $N_E$ snippets are associated with 88
Qualitas projects. We encountered NiCad failures with a few Qualitas
projects.~$N_D$ could not detect clones in \textsf{hibernate} due to
clustering errors. $N_E$ generated renaming errors \FIXME{What are
  renaming errors?}  for 5 projects including \textsf{vuze},
\textsf{hibernate}, \textsf{myfaces}, \textsf{netbeans}, and
\textsf{spring}. We have contacted the creator of NiCad regarding the
issues. They identified the issues as problems in the TXL grammar and
as problems of long file paths, and will be fixed in the next NiCad
releases.

@@

We had in total 31,946 online clone pair candidates for classifications. 2,308 and 11,749 were \textit{good} and \textit{ok} clone pairs respectively. 17,801 and 88 clone pairs are from $S_D$ and $N_D$ after the filtering. Please note that we ignored 20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to their large number of clones and the very small average clone sizes of 4.79 and 5.33 lines (see \Cref{tab:raw_stats}). They had a high probability to be trivial clones.

Before performing manual classification, we used regular expressions to automatically classify {\small\texttt{equals()}} and the remaining getters/setters. As shown in \Cref{tab:online_clone_classification_results}, the automatic classifier helped us classified and captured 28,314 clone pairs into pattern BP.

>>>>

\begin{figure*}
	\begin{lstlisting}
          /* Code in Stack Overflow post ID 22315734 */                  /* WritableComparator.java (2016-09-26) */
          public int compare(byte[] b1,int s1,int l1,                    public int compare(byte[] b1,int s1,int l1,
                             byte[] b2,int s2,int l2) {                                     byte[] b2,int s2,int l2) {
            try {                                                          try {
              buffer.reset(b1,s1,l1); /* parse key1 */                       buffer.reset(b1,s1,l1); /* parse key1 */
              key1.readFields(buffer);                                       key1.readFields(buffer);
              buffer.reset(b2,s2,l2); /* parse key2 */                       buffer.reset(b2,s2,l2); /* parse key2 */
              key2.readFields(buffer);                                       key2.readFields(buffer);
            } catch (IOException e) {                                        buffer.reset(null,0,0); /* clean up reference */
              throw new RuntimeException(e);                               } catch (IOException e) {
            }                                                                throw new RuntimeException(e);
            return compare(key1,key2); /* compare them */                  }
          }                                                                return compare(key1, key2); /* compare them */
	                                                                       }
	\end{lstlisting}
	\caption{A motivating example of the two code fragments of
          {\small\texttt{WritableComparator.java}}. The one from the
          Stack Overflow post 22315734 (left) is outdated when compared to
          its latest version in the \textsf{hadoop} code base
          (right).}
	\label{fig:before-after}
\end{figure*}

@@

We were aware of effects of configurations to clone detection results
and the importance of searching for optimised configurations in
empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space
of at least 15 Simian and 5 NiCad parameters, we are unable to search
for the best configurations of the tools. Thus, we decided to
configure Simian and NiCad using two established configurations:
(1)~the tools' default configurations chosen by the tools' creators
(denoted as \textit{D}), and (2)~the discovered configurations for
Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
of optimising clone detectors' configurations based on clone agreement
(denoted by \textit{E}). The details of the two configurations are
described in \Cref{t:param_tuning}.

@@

Having two clone detectors, Simian
(denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two
chosen configurations (\textit{D} and \textit{E}) each, we used
Bellon's good and ok-match for agreement in four possible pair-wise
combinations: $S_{D}$--$N_{D}$, $S_{D}$--$N_{E}$, $S_{E}$--$N_{D}$,
and $S_{E}$--$N_{E}$.

@@

The statistics on clones obtained from running Simian and NiCad are
presented in \Cref{tab:raw_stats}. Simian in the default configuration
($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
144,064 Stack Overflow snippets, associated with 92 Qualitas
projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
snippets containing clones associated with 111 Qualitas
projects. NiCad in the default configuration ($N_D$) reported clones
between 1,392 Stack Overflow code snippets and 82 Qualitas
projects. NiCad in the EvaClone configuration ($N_E$) reported the
largest number of 12,886 cloned snippets mainly due to the more
relaxed configuration. The $N_E$ snippets are associated with 88
Qualitas projects. We encountered NiCad failures with a few Qualitas
projects.~$N_D$ could not detect clones in \textsf{hibernate} due to
clustering errors. $N_E$ generated errors during code normalisation by 
variable renaming for 5 projects including \textsf{vuze},
\textsf{hibernate}, \textsf{myfaces}, \textsf{netbeans}, and
\textsf{spring}. We have contacted the creator of NiCad regarding the
issues. They identified the issues as problems in the TXL grammar and
as problems of long file paths, and will be fixed in the next NiCad
releases.

@@

We had in total 31,946 online clone pair candidates for classifications. 2,308 and 11,749 were \textit{good} and \textit{ok} clone pairs respectively. 17,801 and 88 clone pairs are from $S_D$ and $N_D$ after the filtering. Please note that we ignored 20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to their large number of clones and the very small average clone sizes of 4.79 and 5.33 lines (see \Cref{tab:raw_stats}). They had a high probability to be trivial clones. 
Before performing manual classification, we used regular expressions to automatically classify {\small\texttt{equals()}} and the remaining getters/setters. As shown in \Cref{tab:online_clone_classification_results}, the automatic classifier helped us classified and captured 28,314 clone pairs into pattern BP.
